Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation

### 2020-07-13 main.tex
Added abstract according to my favourite 6 point method Added keywords Continued planning intro/problem/literature sections and orders

%=================================================================
% Full title of the paper (Capitalized)
\Title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Partially Homomorphic Aggregation}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: Place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: Describe briefly the main methods or treatments applied; (3) Results: Summarize the article's main findings; and (4) Conclusion: Indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}

@@

Additionally encoding for signal processing is an issue. Typically unlimited scalar multiplications and additions using a scheme that allows it over integers does not work on encoded real numbers. Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication.

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy. Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy. Existing secure methods fail to address sensor and navigator privacy in some common model-based non-linear measurement localisation methods forfeiting broad applicability. We define a novel, cryptographically secure, weighted aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation. The requirements and cryptographic proof are given for the weighted aggregation scheme, and simulations of the private filter are used to evaluate the accuracy and performance of the method. Our approach defines a novel, computationally plausible, and private model-based localisation filter with direct application to environments where nodes may not be fully trusted, and data is considered sensitive.}

% Keywords
\keyword{Extended Kalman Filter; Secure Localisation; Private Aggregation}

@@

Additionally encoding for signal processing is an issue. Typically unlimited scalar multiplications and additions using a scheme that allows it over integers does not work on encoded real numbers. Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication (extendable to more but each further limits the real number size and increases risk of overflow).
